Hunting experience shapes individual foraging specialization and predator-prey interactions in an online videogame

### 2023-03-10 manuscript/Chapter2-manuscript.Rmd
knitted the changes

Keywords: foraging behaviour, individual specialization, learning, behavioural plasticity, prey predictability, online videogames

@@

```{r, eval=FALSE}

# =======================================================================

# Extract the correlations to report values in the text

# =======================================================================

# =======================================================================
# Prepare the draws
# =======================================================================

 # Model
 path <- here::here("outputs", "02_outputs_models")
 fit <- readRDS(file.path(path, "02B_DHMLM.rds"))

 # Extract the draws
 draws <- data.table(
     as_draws_df(
         fit,
         variable = c("cor"),
         regex = TRUE)
 )

 draws[, c(106:109) := NULL]

 # =======================================================================
 # =======================================================================

 # =======================================================================
# 2. Transform the draws table
# =======================================================================

# Reshape the table -----------------------------------------------------

 # Long format
 table <- melt(draws,
               measure = patterns("^cor_predator_id"),
               variable.name = "correlation")

 # Summarize the values (means + 95% CI) ---------------------------------

 # Intervals
 lower_interval <- function (x) {coda::HPDinterval(as.mcmc(x), 0.95)[1]}
 upper_interval <- function (x) {coda::HPDinterval(as.mcmc(x), 0.95)[2]}

 table[, ":=" (mean = mean(value),
               lower_ci = lower_interval(value),
               upper_ci = upper_interval(value)),
       by = .(correlation)]

 cor_tab <- unique(table[, c(1, 3:5)])

 # Round values to 3 digits
 cor_tab[, c(2:4) := lapply(.SD, function (x) {round(x, digits = 3)}),
         .SDcols = c(2:4)]

# =======================================================================
# =======================================================================

@@

Empirical studies in humans and animals show that proficiency in a given task often increases nonlinearly with experience, and stabilizes when an expert level is reached [reviewed in @Dukas2019]. However, these patterns are derived from models that assume the same increase in expertise for each individual, and their data do not include repeated measures of individual success through time. In contrast with these studies, our analyses revealed that there was no population increase in expertise; instead, individual predators in *DBD* displayed distinct patterns of expertise acquisition. For instance, many predators increased their success (Figure S1A), but others displayed a decrease in success (Figure S1B) or no change in success at all with experience. We predicted that this would occur because predators should differ in the type of prey that they encounter, as some may be easier to capture than others. This is often the case in nature as prey can use variety of defenses such as physical armaments, toxins, camouflage, or antipredator behaviours to escape predation [@BrodieIII.BrodieJr.1999;@Bowen.etal2002;@brodieCoEvolutionPredatorsPrey2010;@Nomura.etal2011;@Carey.Wahl2011]. However, our results show that the speed of the prey did not shape individual differences in skill aquisition by predators, even if they differed in the prey that they encountered. This was unexpected, because prey speed is an important predictor of predator success in this system [@FraserFranco.etal2022] as well as in others [@Walker.etal2005;@Kelley.Magurran2011]. Despite that other antipredator tactics may mediate these individual responses by predators, it is likely that individual differences in motivation and perseverance, attention span, or memory retention were also major causes [@Warburton2003;@morand-ferronStudyingEvolutionaryEcology2016;@Dukas2019]. For instance, a persevering predator may increase its success much more steadily than an unmotivated predator that quickly abandons a chase. Another factor that may explain differences in the development of expertise is the time delay between hunting events, such that a predator that played 300 matches in the span of six months may not retain information (e.g. prey escape patterns or muscle memory) as well as one that played 300 matches in the span of 6 days. While this has not been tested yet in a predator-prey interaction, it is hypothesized that a greater delay between exposure events should attenuate or even negate the relationship between cumulative experience and success as a result of forgetting [@Endler1991;@Wright.etal2022].

@@

*je peux commencer à plug le arms race dans ce paragraphe.*
*il faut aussi que je parle du fait que la variation dans le succès de capture a diminué avec l'XP*
*- Experience strengthens predator-prey interactions*
*- Experience dampens the relationship between behaviour and success*

>>>>

Keywords: foraging behaviour, individual specialization, behavioural plasticity, learning, prey predictability, virtual ecology

@@

@@

Empirical studies in humans and animals show that proficiency in a given task often increases nonlinearly with experience, and stabilizes when an expert level is reached [reviewed in @Dukas2019]. However, these patterns are derived from models that assume the same increase in expertise for each individual, and their data do not include repeated measures of individual success through time. In contrast with these studies, our analyses revealed that there was no population increase in expertise; instead, individual predators in *DBD* displayed distinct patterns of expertise acquisition. For instance, many predators increased their success (Figure S1A), but others displayed a decrease in success (Figure S1B) or no change in success at all with experience. We predicted that this would occur because predators should differ in the type of prey that they encounter, as some may be easier to capture than others. This is often the case in nature as prey can use variety of defenses such as physical armaments, toxins, camouflage, or antipredator behaviours to escape predation [@BrodieIII.BrodieJr.1999;@Bowen.etal2002;@brodieCoEvolutionPredatorsPrey2010;@Nomura.etal2011;@Carey.Wahl2011]. However, our results show that the speed of the prey did not shape individual differences in skill acquisition by predators, even if they differed in the prey that they encountered. This was unexpected, because prey speed is an important predictor of predator success in this system [@FraserFranco.etal2022] as well as in others [@Walker.etal2005;@Kelley.Magurran2011]. Despite that other antipredator tactics may mediate these individual responses by predators, it is likely that individual differences in motivation and perseverance, attention span, or memory retention were also major causes [@Warburton2003;@morand-ferronStudyingEvolutionaryEcology2016;@Dukas2019]. For instance, a persevering predator may increase its success much more steadily than an unmotivated predator that quickly abandons a chase. Another factor that may explain differences in the development of expertise is the time delay between hunting events, such that a predator that played 300 matches in the span of six months may not retain information (e.g. prey escape patterns or muscle memory) as well as one that played 300 matches in the span of 6 days. While this has not been formally tested, it is hypothesized that a greater delay between exposure events should attenuate or even negate the relationship between cumulative experience and success as a result of forgetting [@Endler1991;@Wright.etal2022].

@@

```{r eval = FALSE}
*je peux commencer à plug le arms race dans ce paragraphe.*
*il faut aussi que je parle du fait que la variation dans le succès de capture a diminué avec l'XP*
*- Experience strengthens predator-prey interactions*
*- Experience dampens the relationship between behaviour and success*
